### 2015-12-29 ch01-intro/introduction.tex
Patching up some references
Voorhoeve2015 in bibliograhy

   \section{Contributions}

@@

The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and 
\begin{itemize}
  \item \fullcite{Geerardyn2014IFAC},
  \item \fullcite{Geerardyn2014ISMA}.
\end{itemize}
Preliminary results have been presented at local (non-refereed) conferences:
\begin{itemize}
  \item \fullcite{Geerardyn2013Benelux},
  \item \fullcite{Geerardyn2013ERNSI},
  \item \fullcite{Geerardyn2014Benelux},
  \item \fullcite{Geerardyn2014DYSCO}, and
  \item \fullcite{Geerardyn2014ERNSI}.
\end{itemize}
The experimental work related to \chapref{sec:hinf} is also presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{SYSID}) and :
\begin{itemize}
  \item \fullcite{Voorhoeve2015}
  \item \fullcite{Voorhoeve2015ERNSI}
\end{itemize}

@@

\begin{itemize}
  \item \fullcite{vanBerkel2014Automatica}
  \item \fullcite{Cooman2012SMACD}
  \item \fullcite{Cooman2012DYSCO}
  \item \fullcite{Cooman2012ERNSI}
\end{itemize}

\end{refsection}

>>>>

@@

The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and 
\begin{itemize}
  \item \fullcite{Geerardyn2014IFAC},
  \item \fullcite{Geerardyn2014ISMA}.
\end{itemize}
Preliminary results have been presented at local (non-refereed) conferences:
\begin{itemize}
  \item \fullcite{Geerardyn2013Benelux},
  \item \fullcite{Geerardyn2013ERNSI},
  \item \fullcite{Geerardyn2014Benelux},
  \item \fullcite{Geerardyn2014DYSCO}, and
  \item \fullcite{Geerardyn2014ERNSI}.
\end{itemize}
The experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{SYSID}) and :
\begin{itemize}
  \item \fullcite{Voorhoeve2015SYSID}
  \item \fullcite{Voorhoeve2015ERNSI}
\end{itemize}

@@

\begin{itemize}
  \item \fullcite{vanBerkel2014Automatica},
  \item \fullcite{Cooman2012SMACD},
  \item \fullcite{Cooman2012DYSCO},
  \item \fullcite{Cooman2012ERNSI}.
\end{itemize}
\end{refsection}
